Bayesian model in JAGS

### 2023-01-23 3_JAGS_Bayesian_model/Jags_Bayesian_model.Rmd
update jags model

```{r,message=FALSE,warning=FALSE}
# Load a shapefile. Make sure each polygon on shapefile  
# corresponds to only one state. 
require(rgdal) # for working with shapefiles
require(ggplot2) # for plot and fortify
CT1map = readOGR(dsn=path.expand('./WGS84'), layer= 'zipct_37800_0000_2010_s100_census_1_shp_wgs84')
CTmap.df <- as.data.frame(CT1map)
CT1map_fort <- fortify(CT1map,region="ZCTA5CE10")
# ZCTA5CE10 is CT zipcode ID
# The ID variable is then the zipcode/area unit 
CT1map_fort$zipcode <- CT1map_fort$id

# Sort both the shapefile and the data file by ID.
# This is the most important step
CTmap.sort <- CT1map[order(CT1map$ZCTA5CE10),]
```

@@

###  Step 2. Create a neighbor matrix from the sorted shapefile 
```{r,message=FALSE}
library(spdep) # for neighbor evaluation

# Neighbors can either be Queen 
# (any zip that touches another zip - even at corners) 
# or Rook neighbors (share full sides -- not corners)

@@

# When data is missing -- there's more non-zero links involved 
# Try to make snap distance as small as possible 
# while making sure all zipcode have at least one neighbor
neighb <- poly2nb(CTmap.sort, queen = T, snap = sqrt(0.001))

# Check average number of links -- increase snap distance 
# if it says there is a zip with zero neighbors
neighb # Avg Number of links = 8.18705

# Make neighbor matrix 
# if zero.policy FALSE stop with error for any empty neighbour sets, 
# if TRUE permit the weights list to be formed with zero-length weights vectors
# B is the basic binary coding, W is row standardised (both are commonly used)
neighb.mat <- nb2mat(neighb, zero.policy = T, style = 'B')
```

@@

###  Step 3. Create a W matrix for Leroux model 
```{r,message=FALSE}
# For Leroux model, neighbor matrix needs to have 0 
# if not neighboring, -1 if neighbor, 
# and number of neighbors for each zip on diagonal), so...
w.mat <- ifelse(neighb.mat==1,-1,neighb.mat)
num.neigh <- colSums(neighb.mat) 
# Count the number of neighbors for each state
for (i in 1:nrow(w.mat)) {
  # Put the number of neighbors on diagonal
  for (j in 1:ncol(w.mat)) {
    if (i==j) {
      w.mat[i,j] <- num.neigh[i]
    }
  }
}
```

>>>>

```{r message=FALSE,warning=FALSE}
# Load a shapefile. Make sure each polygon on shapefile  
# corresponds to only one state. 
require(rgdal) # for working with shapefiles
require(ggplot2) # for plot and fortify
CT1map = readOGR(dsn=path.expand('./WGS84'), 
layer= 'zipct_37800_0000_2010_s100_census_1_shp_wgs84')
CTmap.df <- as.data.frame(CT1map)
CT1map_fort <- fortify(CT1map,region="ZCTA5CE10")
# ZCTA5CE10 is CT zipcode ID
# The ID variable is then the zipcode/area unit 
CT1map_fort$zipcode <- CT1map_fort$id
```

@@

###  Step 2. Find the number of neighbors from the sorted shapefile  
```{r,message=FALSE}
# Sort both the shapefile and the data file by ID.
# This is the most important step
CTmap.sort <- CT1map[order(CT1map$ZCTA5CE10),]

library(spdep) # for neighbor evaluation 
# Neighbors can either be Queen 
# (any zip that touches another zip - even at corners) 
# or Rook neighbors (share full sides -- not corners)

@@

# When data is missing -- there's more non-zero links involved 
# Try to make snap distance as small as possible 
# while making sure all zipcode have at least one neighbor
neighb <- poly2nb(CTmap.sort, queen = T, snap = sqrt(0.001))
```

@@

###  Step 3. Create a neighbor matrix with 1 suggesting adjacency 
```{r,message=FALSE}
# Check average number of links -- increase snap distance 
# if it says there is a zip with zero neighbors
neighb # Avg Number of links = 8.18705

# Make neighbor matrix 
# if zero.policy FALSE,
# stop with error for any empty neighbor sets, 
# if TRUE, permit the weights list to be
# formed with zero-length weights vectors
# B is the basic binary coding, 
# W is row standardised (both are commonly used)
neighb.mat <- nb2mat(neighb, zero.policy = T, style = 'B')
```

###  Step 3. Create the W matrix for Leroux model 
```{r,message=FALSE}
# For Leroux model, neighbor matrix needs to have 0 
# if not neighboring, -1 if neighbor, 
# and number of neighbors for each zip on diagonal), so...
w.mat <- ifelse(neighb.mat==1,-1,neighb.mat)
num.neigh <- colSums(neighb.mat) 
# Count the number of neighbors for each state
for (i in 1:nrow(w.mat)) {
  # Put the number of neighbors on diagonal
  for (j in 1:ncol(w.mat)) {
    if (i==j) {
      w.mat[i,j] <- num.neigh[i]
    }
  }
}
```
